Privacy-Respecting Type Error Telemetry at Scale

### 2024-02-09 programming23/paper.tex
luau ++
orcid, biber, final touch ups

\usepackage{alltt}
% Not sure why <Programming> is recommending non-standard tools
% \usepackage[backend=biber]{biblatex}
\usepackage[export]{adjustbox}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{colortbl}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
% Errors with
% ! Undefined control sequence.
% <argument> \l__siunitx_number_implicit_plus_bool 
% l.61 \begin{document}
% using Mac TeXlive 20230313_2
% \usepackage{siunitx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{wasysym}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

\author[a,b]{Ben Greenman}
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) was a CIFellows 2020
postdoc at Brown University and is now an assistant professor in the
Kahlert School of Computing at the University of Utah.}
% \orcid{0000-0001-7078-9287}
\affiliation[a]{Brown University, Providence, RI, USA}
\affiliation[b]{University of Utah, Salt Lake City, UT, USA}

\author[c]{Alan Jeffrey}
\authorinfo{(\email{ajeffrey@roblox.com}) is a Principal Software Engineer at Roblox.}
% \orcid{0000-0001-6342-0318}
\affiliation[c]{Roblox, San Mateo, CA, USA}

\author[a]{Shriram Krishnamurthi}
% \orcid{0000-0001-5184-1975}
\authorinfo{(\email{shriram@brown.edu}) is the Vice President of Programming Languages (no, not really) at Brown University.}

\author[c]{Mitesh Shah}
% \orcid{0009-0000-6084-123X}
\authorinfo{(\email{mshah@roblox.com}) is Senior Engineering Director, Programmability, at Roblox.}

@@

Creators can opt in to detailed error reports and highlights by
choosing a \emph{type analysis mode} for each script.
The modes are:
\begin{itemize}
  \item \mnocheck{}: report only syntax errors (the default),
  \item \mnonstrict{}: report syntax errors and a subset of high confidence type errors, and
  \item \mstrict{}: report syntax errors and all type errors.
\end{itemize}
Each run of the type analysis can report several errors.
There is no guarantee that creators read every error.
In fact, creators who close the Script Analysis widget
can see highlights in their code but no further details about the errors.

@@

The type error telemetry for a Roblox Studio session is gathered as a series of
records, all with the same  \panon{} session identifier.
This allows us to correlate telemetry across a single
session, but not between sessions.
In order to avoid swamping the telemetry servers, the client reports on a subset
of telemetry events via two levels of uniform random sampling:
\begin{itemize}
  \item
    1\% of Roblox Studio sessions generate \emph{any} type error telemetry, and
  \item
    0.5\% of all type analyses (approximately 1 in 200 keystrokes)
    in an enrolled session generate a telemetry record.
\end{itemize}
In addition to sending telemetry for randomly-selected keystrokes,
our system sends a telemetry record every time the session changes
focus from one module to another.
These records provide important context for mode switches:
if one record uses \mstrict{} mode but the next uses \mnocheck{},
then it is critical to know whether the creator downgraded modes
or simply switched to another module.

@@

The artifact for this paper contains the full telemetry dataset
and scripts for reproducing the analysis in~\cref{s:data}.
The source code for the paper itself is available through Software
Heritage~\cite{luau-swhid}.

@@

\bibliography{bib}

>>>>

\usepackage{alltt}
% Not sure why <Programming> is recommending non-standard tools
% uncomment because publisher asked about missing URL access dates
\usepackage[backend=biber]{biblatex}
\usepackage[export]{adjustbox}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{colortbl}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
% Errors with
% ! Undefined control sequence.
% <argument> \l__siunitx_number_implicit_plus_bool 
% l.61 \begin{document}
% using Mac TeXlive 20230313_2
% \usepackage{siunitx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{wasysym}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

\addbibresource{bib.bib}

@@

\author[a,b]{Ben Greenman}[0000-0001-7078-9287]
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) was a CIFellows 2020
postdoc at Brown University and is now an assistant professor in the
Kahlert School of Computing at the University of Utah.}
\affiliation[a]{Brown University, Providence, RI, USA}
\affiliation[b]{University of Utah, Salt Lake City, UT, USA}

\author[c]{Alan Jeffrey}[0000-0001-6342-0318]
\authorinfo{(\email{ajeffrey@roblox.com}) is a Principal Software Engineer at Roblox.}
\affiliation[c]{Roblox, San Mateo, CA, USA}

\author[a]{Shriram Krishnamurthi}[0000-0001-5184-1975]
\authorinfo{(\email{shriram@brown.edu}) is the Vice President of Programming Languages (no, not really) at Brown University.}

\author[c]{Mitesh Shah}[0009-0000-6084-123X]
\authorinfo{(\email{mshah@roblox.com}) is Senior Engineering Director, Programmability, at Roblox.}

@@

Creators can opt in to detailed error reports and highlights by
selecting a \emph{type analysis mode} for each script.
There are three modes that creators may choose from:
\begin{itemize}
  \item \mnocheck{}: report only syntax errors (the default),
  \item \mnonstrict{}: report syntax errors and a subset of high confidence type errors, and
  \item \mstrict{}: report syntax errors and all type errors.
\end{itemize}
Each run of the type analysis can report several errors.
There is no guarantee that creators read every error.
In fact, creators who close the Script Analysis widget
can see highlights in their code but no further details about the errors.

@@

The type error telemetry for a Roblox Studio session is gathered as a series of
records, all with the same  \panon{} session identifier.
This allows us to correlate telemetry across a single
session, but not between sessions.
In order to avoid swamping the telemetry servers, the client reports on a subset
of telemetry events via two levels of uniform random sampling:
\begin{itemize}
  \item
    \pct{1} of Roblox Studio sessions generate \emph{any} type error telemetry, and
  \item
    \pct{0.5} of all type analyses (approximately 1 in 200 keystrokes)
    in an enrolled session generate a telemetry record.
\end{itemize}
In addition to sending telemetry for randomly-selected keystrokes,
our system sends a telemetry record every time the session changes
focus from one module to another.
These records provide important context for mode switches:
if one record uses \mstrict{} mode but the next uses \mnocheck{},
then it is critical to know whether the creator downgraded modes
or simply switched to another module.

@@

The artifact for this paper contains the full telemetry dataset
and scripts for reproducing the analysis in~\cref{s:data}.

@@

{

\printbibliography
}
